Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-03-11 manuscript/supplementaryRW.Rmd
deletes significanve obs and H7cm and 10cm tables in suplmentary

## Recruitment levels

@@

kable(zeroInflated,  format = "latex", caption = "Number of total samples, samples with zero recruitment and the proportion of zero recruitment per model and observed data.")|>
        kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

## Model complexity

Summary of the linear model of the overestimation proportions versus the
mean complexity value on the establishment module.

```{r tableComp, echo=FALSE,  message=FALSE, render = 'normal_print'}
library(knitr)

tableCompOver <- readr::read_csv(here::here("figures", "tableCompOver.csv"))
jtools::summ(lm(overestimation ~ complexity, data = tableCompOver), model.info = FALSE, digits = 5)

@@

```{r sigH7_Obs, echo=FALSE,  message=FALSE}
library(knitr)

sigDiff7 <- readr::read_csv(here::here("figures", "sigH7_Obs.csv"))

kable(sigDiff7,  format = "latex", caption = "Test of the significance of the differences of Shannon index between the observed data and each model for 7cm threshold.") |>
        #kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

```{r sigH10_Obs, echo=FALSE,  message=FALSE}
library(knitr)

sigDiff10 <- readr::read_csv(here::here("figures", "sigH10_Obs.csv"))

kable(sigDiff10,  format = "latex", caption = "Test of the significance of the differences of Shannon index between the observed data and each model for 10cm threshold.") |>
        #kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

>>>>

## Ingrowth levels, tree diversity and mortality in tree establishment

@@

kable(zeroInflated,  format = "latex", caption = "Number of total samples, samples with zero recruitment and the proportion of zero recruitment per model and observed data.")|>
        #kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

@@

## Model traits and model performance

### Model complexity VS overestimation

```{r plotComp, echo=FALSE, warning=FALSE, fig.cap="Plot and summary statistics of the linear model between the overestimation proportion in ingrowth levels and the mean complexity value of the establisment modules", fig.show = 'hold', out.width = '70%'}

knitr::include_graphics(here::here("figures", "compOver.png"))

## Total ingrowth and individual species regeneration niches
